### 2013-08-23 doc/dissertation/document/chapters/parallel_mc/parallel_mc.tex
spell check for parallel chapter

\subsection{Parallel FANM Implementation}
\label{subsec:parallel_fanm}
Here we briefly comment on how a FANM method may be implemented in
parallel. A parallel FANM method relies on a basic set of parallel
matrix-vector operations outlined in
\S~\ref{sec:parallel_krylov_methods} as well as the global residual
and Jacobian assembly procedure described in
\S~\ref{subsec:automatic_differentiation}. Consider the FANM iteration
scheme in Algorithm~\ref{alg:fanm}. We must first assemble the linear
system in parallel through the element-wise function evaluations to
generate both the global Jacobian operator and the global nonlinear
residual vector on the right hand side. Per Bartlett's work on
automatic differentiation, efficient and automated parallel mechanisms
are available to do this through a sequence of scatter/gather
operations. With these tools available for residual and Jacobian
generation, the remainder of the parallel procedure is simple. The
linear Newton correction system is solved using the parallel MCSA
method as described in the previous section and the Newton correction
applied to the previous iterate's solution through a parallel vector
update with parallell norm operations applied to check for
convergence.

@@

This result is significant in that it shows a solution technique in
which the linear problem can actually be replicated and enhance time
to solution, something that cannot be achieved with conventional
methods. At larger core counts, however, this reduction in compute
time is not as large due to the fact that the tally reduction across
blocks requires more resources and those resources are clearly growing
with core count (most obviously in the 4 set case with split
histories). In addition, at 131,072 cores for the largest 4 set
computation, processors that share a block may be some physical
distatance from one another in the machine, adding to latency and
decreasing performance.

>>>>

\subsection{Parallel FANM Implementation}
\label{subsec:parallel_fanm}
Here we briefly comment on how a FANM method may be implemented in
parallel. A parallel FANM method relies on a basic set of parallel
matrix-vector operations outlined in
\S~\ref{sec:parallel_krylov_methods} as well as the global residual
and Jacobian assembly procedure described in
\S~\ref{subsec:automatic_differentiation}. Consider the FANM iteration
scheme in Algorithm~\ref{alg:fanm}. We must first assemble the linear
system in parallel through the element-wise function evaluations to
generate both the global Jacobian operator and the global nonlinear
residual vector on the right hand side. Per Bartlett's work on
automatic differentiation, efficient and automated parallel mechanisms
are available to do this through a sequence of scatter/gather
operations. With these tools available for residual and Jacobian
generation, the remainder of the parallel procedure is simple. The
linear Newton correction system is solved using the parallel MCSA
method as described in the previous section and the Newton correction
applied to the previous iterate's solution through a parallel vector
update with parallel norm operations applied to check for
convergence.

@@

This result is significant in that it shows a solution technique in
which the linear problem can actually be replicated and enhance time
to solution, something that cannot be achieved with conventional
methods. At larger core counts, however, this reduction in compute
time is not as large due to the fact that the tally reduction across
blocks requires more resources and those resources are clearly growing
with core count (most obviously in the 4 set case with split
histories). In addition, at 131,072 cores for the largest 4 set
computation, processors that share a block may be some physical
distance from one another in the machine, adding to latency and
decreasing performance.
